---
title: "exex_ORL_recovery"
output: html_document
date: '2023-12-29'
---
Loading packages
```{r}
install.packages("pacman")
pacman::p_load(R2jags, parallel, ggpubr, extraDistr, truncnorm)

pacman::p_load(ggplot, ggplot2, ggpubr)
```

Setting seed and practicalities 
```{r}
set.seed(1983)

# defining a function for calculating the maximum of the posterior density (not exactly the same as the mode)
MPD <- function(x) {
  density(x)$x[which(density(x)$y==max(density(x)$y))]
}
```

Task environment. In the exploration/exploitation task there are two trial types. There is a choice between a (1) lucrative and informative detrimental and non-informative, (2) detrimental and informative, lucrative and non-informative. And in each trial you have to choose between either in each trial. In run 1 trials where shifted at trial [19, 23, 21, 17] and run 2 [23, 19,17, 21]

##Setting up payoff structure
```{r}
# Mimicking data from study, with 80 trials (2 times for each participant 160 trials total), 50% chance for information choice = lucrative choice
ntrials <- 80  

# Setting up empty array to be filled
reward <- array(NA, dim = c(ntrials, 2))

# Rewards for different probabilities
probabilities <- list(
  prob1 = rbinom(19, 1, 0.85),
  prob2 = rbinom(23, 1, 0.85),
  prob3 = rbinom(21, 1, 0.85),
  prob4 = rbinom(17, 1, 0.85)
)

# Initialize the start row for appending
start_row <- 1

# Loop to fill the payoff array
for (i in seq_along(probabilities)) {
  L <- probabilities[[i]] + probabilities[[i]] - 1
  R <- L * (-1)
  
  # Switch L and R for each new probability
  if (i %% 2 == 0) {
    temp <- L
    L <- R
    R <- temp
  }
  
  # Determine the number of rows for the current probability
  num_rows <- length(L)
  
  # Append values to the payoff array
  reward[start_row:(start_row + num_rows - 1), ] <- cbind(L, R)
  
  # Update the start row for the next probability
  start_row <- start_row + num_rows
}

```

```{r}
# Initialize an empty array
info <- array(NA, dim = c(ntrials, 2))

# Loop to fill the array
for (i in 1:ntrials) {
  # Allocate "x" or "y" with a 50% chance for each row
  if (runif(1) <= 0.5) {
    info[i, ] <- c(2, 1)
  } else {
    info[i, ] <- c(1, 2)
  }
}

payoff <- reward*info
#Setting info nr 1 as the info choice for deck 1 and then make the simulation always choose deck 1 
#info[1,1] <- 2
#info[1,2] <- 1

#payoff <- cbind(reward, c(2), c(1)) # deck 1 and 2 reward and loss shapes with flips, deck 3 info, deck 4 no info
```

```{r}
set.seed(2000)
a_rew <- .3
a_pun <- .1
K <- 1
theta <- 1
omega_p <- .1
omega_f <- .3 

ntrials <- 80

source("exex_ORL_simulations.R")
ORL_sims <- ORL_sim(payoff,ntrials,a_rew,a_pun,K,theta,omega_p, omega_f)

par(mfrow=c(3,2))
plot(ORL_sims$Ev[,1])
plot(ORL_sims$Ev[,2])
plot(ORL_sims$I[,1])
plot(ORL_sims$I[,2])
plot(ORL_sims$X)
plot(ORL_sims$PS[,1])
plot(ORL_sims$PS[,2])
plot(ORL_sims$p[,1])
plot(ORL_sims$p[,2])

par(mfrow=c(2,2))
plot(abs(ORL_sims$Ev[,1]-ORL_sims$Ev[,2]))
plot(ORL_sims$X)
plot(ORL_sims$I[,1])
plot(ORL_sims$I[,2])

```


```{r}
x <- ORL_sims$x
X <- ORL_sims$X

# set up jags and run jags model
data <- list("x","X","ntrials", "payoff") 
params<-c("a_rew","a_pun","K","theta","omega_p")
samples <- jags.parallel(data, inits=NULL, params,
                model.file ="exex_ORL_agent.txt", n.chains=3, 
                n.iter=5000, n.burnin=1000, n.thin=1, n.cluster=3)
```


```{r}
###--------------Run full parameter recovery -------------
niterations <- 100 # fewer because it takes too long

true_a_rew <- array(NA,c(niterations))
true_a_pun <- array(NA,c(niterations))
true_K <- array(NA,c(niterations))
true_theta <- array(NA,c(niterations))
true_omega_f <- array(NA,c(niterations))
true_omega_p <- array(NA,c(niterations))

infer_a_rew <- array(NA,c(niterations))
infer_a_pun <- array(NA,c(niterations))
infer_K <- array(NA,c(niterations))
infer_theta <- array(NA,c(niterations))
infer_omega_f <- array(NA,c(niterations))
infer_omega_p <- array(NA,c(niterations))

start_time = Sys.time()

for (i in 1:niterations) {
  
  # let's see how robust the model is. Does it recover all sorts of values?
  a_rew <- runif(1,0,1)
  a_pun <- runif(1,0,1)
  K <- runif(1,0,2)
  theta <- runif(1,.2,3) # could also just be a set value (e.g. 1) to simplify the model a bit
  omega_f <- runif(1,0,1)
  omega_p <- runif(1,-2,2)
  
  ORL_sims <- ORL_sim(payoff,ntrials,a_rew,a_pun,K,theta,omega_p, omega_f)
  
  x <- ORL_sims$x
  X <- ORL_sims$X
  
  # set up jags and run jags model
  data <- list("x","X","ntrials", "payoff") 
  params<-c("a_rew","a_pun","K","theta","omega_p", "omega_f")
  samples_recovery <- jags.parallel(data, inits=NULL, params,
                  model.file ="exex_ORL_agent.txt", n.chains=3, 
                  n.iter=3000, n.burnin=1000, n.thin=1, n.cluster=3)
  
  
  true_a_rew[i] <- a_rew
  true_a_pun[i] <- a_pun
  true_K[i] <- K
  #true_theta[i] <- theta
  true_omega_f[i] <- omega_f
  true_omega_p[i] <- omega_p
  
  # find maximum a posteriori
  Y <- samples_recovery$BUGSoutput$sims.list
  infer_a_rew[i] <- MPD(Y$a_rew)
  infer_a_pun[i] <- MPD(Y$a_pun)
  infer_K[i] <- MPD(Y$K)
  #infer_theta[i] <- MPD(Y$theta)
  infer_omega_f[i] <- MPD(Y$omega_f)
  infer_omega_p[i] <- MPD(Y$omega_p)

  print(i)
  
}

end_time = Sys.time()
end_time - start_time

# let's look at some scatter plots

par(mfrow=c(3,2))
plot(true_a_rew,infer_a_rew)
plot(true_a_pun,infer_a_pun)
plot(true_K,infer_K)
#plot(true_theta,infer_theta)
plot(true_omega_f,infer_omega_f)
plot(true_omega_p,infer_omega_p)

# plotting code courtesy of Lasse
source('recov_plot.R')
pl1 <- recov_plot(true_a_rew, infer_a_rew, c("true a_rew", "infer a_rew"), 'smoothed linear fit')
pl2 <- recov_plot(true_a_pun, infer_a_pun, c("true a_pun", "infer a_pun"), 'smoothed linear fit')
pl3 <- recov_plot(true_K, infer_K, c("true K", "infer K"), 'smoothed linear fit')
#pl4 <- recov_plot(true_theta, infer_theta, c("true theta", "infer theta"), 'smoothed linear fit')
pl5 <- recov_plot(true_omega_f, infer_omega_f, c("true omega_f", "infer omega_f"), 'smoothed linear fit')
pl6 <- recov_plot(true_omega_p, infer_omega_p, c("true omega_p", "infer omega_p"), 'smoothed linear fit')
ggarrange(pl1, pl2, pl3, pl5, pl6)

# for investigating multi-colinearity

# par(mfrow=c(2,2))
# plot(true_a_rew,true_a_pun)
# plot(infer_a_rew,infer_a_pun)
# plot(true_omega_f,true_omega_p)
# plot(infer_omega_f,infer_omega_p)
# 
# par(mfrow=c(2,2))
# plot(true_a_rew,true_omega_f)
# plot(infer_a_rew,infer_omega_f)
# plot(true_a_rew,true_omega_p)
# plot(infer_a_rew,infer_omega_p)
```

